Stack Safety is a Security Property

### 2021-04-15 tex/main.tex
Minor changes

Our stack-safety criteria depend
critically on the notions of ``call'' and ``return,'' which are not fully explicit
in machine code---the same instruction opcode may be used in some places as part of
a call or return sequence and in other places for other purposes.
%
So we assume we are given a machine language program {\em annotated} with the locations of
instructions representing calls, returns, and function entry points\BCP{I
  still want to talk about whether returns and entry points need to be
  annotated.  To me, these annotations do not make intuitive sense: it is
  the caller's responsibility to know whether the address that it is calling
is really an entry point, and we can trust it to check this.  Similarly, it
is not the callee's role to say when it is returning; it is the caller's
prerogative to decide when it has been returned to!  I.e., from the caller's
point of view, it has been returned to when control resumes at the
instruction following the call with the SP reset to where it was at the
point of the call. (This is the point where it wants to be able to access
its own local state again and expected to find it unmolested.)}. Although these
annotations would typically come from a compiler together with the machine code,
we do not assume anything about their provenance.

\bcp{Can this be postponed to the formal sections?}We further parameterize over the structure of the stack, particularly the means by
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention}, which maps a machine state to a set of addresses.
If a state's \(\PCname\) is annotated as a call, the sealing convention tells us
which addresses must be protected until the return.

@@

This section will elucidate the intuition behind the properties through a series
of examples. Existing stack safety enforcement work mostly refers directly to examples
of bad behavior that it prevents; we will insert our model between the enforcement and
the examples\bcp{Didn't understand that}, arguing that:

@@

>>>>

Our stack-safety criteria depend
critically on the notions of ``call'' and ``return,'' which are not fully explicit
in machine code---the same instruction opcode may be used in some places as part of
a call or return sequence and in other places for other purposes.
%
So we assume we are given a machine language program {\em annotated} with the locations of
instructions representing calls.%, returns, and function entry points\BCP{I
%  still want to talk about whether returns and entry points need to be
%  annotated.  To me, these annotations do not make intuitive sense: it is
%  the caller's responsibility to know whether the address that it is calling
%is really an entry point, and we can trust it to check this.  Similarly, it
%is not the callee's role to say when it is returning; it is the caller's
%prerogative to decide when it has been returned to!  I.e., from the caller's
%point of view, it has been returned to when control resumes at the
%instruction following the call with the SP reset to where it was at the
%point of the call. (This is the point where it wants to be able to access
%its own local state again and expected to find it unmolested.)}.
Although these
annotations would typically come from a compiler together with the machine code,
we do not assume anything about their provenance.

@@

This section will elucidate the intuition behind the properties through a series
of examples. Existing stack safety enforcement work mostly refers directly to examples
of bad behavior that it prevents; we will argue that:

@@

We parameterize over the structure of the stack, particularly the means by
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention}, \(\sealcon \subseteq \MACHS \times \COMPONENTS\), which
maps a machine state to a set of addresses.
If a state's \(\PCname\) is annotated as a call, the sealing convention tells us
which addresses must be protected until the return. Similarly, we abstract over what
it means to return with a {\em return convention}, \(\retcon \subseteq \MACHS \times \MACHS\),
which relates
